Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-10 analysis/Study1.qmd
typos

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)

@@

df4$MAIA_AttentionReg <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
df4$MAIA_BodyTrusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
df4$MAIA_SelfReg<- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
```

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = MAIA_NOTICING, MAIA_NotDistracting = MAIA_NON_DISTRACTING,
    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionReg = mAIA_ATTENTION_REGULATION,
    MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
  )

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = maiaNotice, MAIA_NotDistracting = maiaNonDistracting,
    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionReg = maiaAttentionRegulation,
    MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
  )

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum
  )
```

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
```

@@

@@

```{r}
df12  <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI"))) |>
   rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, 
    MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation
  ) |>
  filter(!is.na(Heart)) |>  # participant is outlier and had total IAS scores below 0.4 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
```

@@

```{r}
#  ONLY IAS DATA
data1a <- select(df1a, all_of(dens1a$Parameter))
data1b <- select(df1b, all_of(dens1b$Parameter))
data2 <- select(df2, all_of(dens2$Parameter))
data3 <- select(df3, all_of(dens3$Parameter))
data6 <- select(df4, all_of(dens4$Parameter))
data5 <- select(df5, all_of(dens5$Parameter))
data6 <- select(df6, all_of(dens6$Parameter))
data7a <- select(df7a, all_of(dens7a$Parameter))
data7b <- select(df7b, all_of(dens7b$Parameter))
data7c <- select(df7c, all_of(dens7c$Parameter))
data8a <- select(df8a, all_of(dens8a$Parameter))
data8b <- select(df8b, all_of(dens8b$Parameter))
data9 <- select(df9, all_of(dens9$Parameter))
data10 <- select(df10, all_of(dens10$Parameter))
data11  <- select(df11, all_of(dens11$Parameter))
data12  <- select(df12, all_of(dens12$Parameter))
data13  <- select(df13, all_of(dens13$Parameter))
data14  <- select(df14, all_of(dens14$Parameter))
data15   <- select(df15, all_of(dens15$Parameter))

data_all <- rbind(
  data1a, data1b, data2, data3, data6, data5, data6, data7a, data7b, data7c,
  mutate(data8a, Tickle = NA), 
  mutate(data8b, Tickle = NA), data9,
  mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
  data11,  data12 , data13, data14, data15  
) 
```

@@

data_allf <- select(data_all, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data1af <- select(data1a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data1bf <- select(data1b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data2f <- select(data2, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data3f <- select(data3, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data5f <- select(data5, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7af <- select(data7a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7bf <- select(data7b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7cf <- select(data7c, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data8af <- select(data8a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data8bf <- select(data8b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data9f <- select(data9, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data10f <- select(data10, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data11f <- select(data11, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data12f <- select(data12, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data13f <- select(data13, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data14f <- select(data14, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data15f <- select(data15, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
```

@@

rez_hclust <- make_hclust(data1af)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cfa1a  <- make_cfa(data1af)

@@

rez_hclust <- make_hclust(data1bf)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cfa1b  <- make_cfa(data1bf)

@@

@@

@@

rez_hclust <- make_hclust(data3f)
rez_ega <- make_ega(data3f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cf3  <- make_cfa(data3f)

@@

@@

@@

@@

@@

@@

rez_hclust <- make_hclust(data5)
rez_ega <- make_ega(data5, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))

@@

@@

rez_hclust <- make_hclust(data5f)
rez_ega <- make_ega(data5f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data5f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cfa5  <- make_cfa(data5f)

@@

@@

rez_cf5$test
```

@@

@@

@@

rez_hclust <- make_hclust(data6f)
rez_ega <- make_ega(data6f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data6f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cf6  <- make_cfa(data6f)

@@

@@

rez_cf6$test
```

@@

@@

@@

@@

@@

@@

@@

@@

rez_cf7b$test
```

@@

@@

@@

@@

rez_cf7c$test
```

@@

@@

@@

@@

rez_cf8a$test
```
::::

@@

@@

@@

>>>>

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)
library(haven)

@@

df4$MAIA_AttentionReg <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
df4$MAIA_SelfReg<- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
```

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = MAIA_NOTICING, MAIA_NotDistracting = MAIA_NON_DISTRACTING,
    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionReg = mAIA_ATTENTION_REGULATION,
    MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) x - 1)) # Original scale 1-6

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = maiaNotice, MAIA_NotDistracting = maiaNonDistracting,
    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionReg = maiaAttentionRegulation,
    MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
```

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
```

@@

df11 <- mutate(df11, across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))))

@@

```{r}
df12  <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI"))) |>
   rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, 
    MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation
  ) |>
  filter(!is.na(Heart)) |>  # participant is outlier and had total IAS scores below 0.4 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
```

@@

```{r}
#  ONLY IAS DATA
data1a <- select(df1a, all_of(dens1a$Parameter))
data1b <- select(df1b, all_of(dens1b$Parameter))
data2 <- select(df2, all_of(dens2$Parameter))
data3 <- select(df3, all_of(dens3$Parameter))
data4 <- select(df4, all_of(dens4$Parameter))
data5 <- select(df5, all_of(dens5$Parameter))
data6 <- select(df6, all_of(dens6$Parameter))
data7a <- select(df7a, all_of(dens7a$Parameter))
data7b <- select(df7b, all_of(dens7b$Parameter))
data7c <- select(df7c, all_of(dens7c$Parameter))
data8a <- select(df8a, all_of(dens8a$Parameter))
data8b <- select(df8b, all_of(dens8b$Parameter))
data9 <- select(df9, all_of(dens9$Parameter))
data10 <- select(df10, all_of(dens10$Parameter))
data11  <- select(df11, all_of(dens11$Parameter))
data12  <- select(df12, all_of(dens12$Parameter))
data13  <- select(df13, all_of(dens13$Parameter))
data14  <- select(df14, all_of(dens14$Parameter))
data15   <- select(df15, all_of(dens15$Parameter))

data_all <- rbind(
  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
  mutate(data8a, Tickle = NA), 
  mutate(data8b, Tickle = NA), data9,
  mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
  data11,  data12 , data13, data14, data15  
) 
```

@@

data_allf <- select(data_all, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data1af <- select(data1a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data1bf <- select(data1b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data2f <- select(data2, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data3f <- select(data3, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data4f <- select(data4, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data5f <- select(data5, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7af <- select(data7a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7bf <- select(data7b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data7cf <- select(data7c, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data8af <- select(data8a, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data8bf <- select(data8b, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data9f <- select(data9, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data10f <- select(data10, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data11f <- select(data11, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data12f <- select(data12, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data13f <- select(data13, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data14f <- select(data14, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
data15f <- select(data15, -Taste, -Affective_touch, -Vomit, -Itch,
                   -Sex_arousal, -Temp)
```

@@

rez_hclust <- make_hclust(data1af)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]]))
rez_cfa1a  <- make_cfa(data1af)

@@

rez_hclust <- make_hclust(data1bf)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1bf, n = 3, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Cough"]], "F4" = colors[["Itch"]]))
rez_cfa1b  <- make_cfa(data1bf)

@@

```{r data3}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data3_details}
#| warning: false
#| message: false

@@

```{r data3f}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

rez_hclust <- make_hclust(data3f)
rez_ega <- make_ega(data3f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cfa3  <- make_cfa(data3f)

@@

```{r data3f_details}
#| warning: false
#| message: false

@@

```{r data4}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data4_details}
#| warning: false
#| message: false

@@

```{r data4f}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data4f_details}
#| warning: false
#| message: false

@@

```{r data5}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

rez_hclust <- make_hclust(data5)
rez_ega <- make_ega(data5, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]]))

@@

```{r data5_details}
#| warning: false
#| message: false

@@

Note: EGA errors.

```{r data5f}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

rez_hclust <- make_hclust(data5f)
# rez_ega <- make_ega(data5f, cols = c(
#   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
#   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data5f, n = 5, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]],
                                            "F5" = colors[["Urinate"]]))
rez_cfa5  <- make_cfa(data5f)

rez_hclust$p / rez_efa$p
```

@@

```{r data5f_details}
#| warning: false
#| message: false

@@

rez_cfa5$test
```

@@

```{r data6}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data6_details}
#| warning: false
#| message: false

@@

```{r data6f}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

rez_hclust <- make_hclust(data6f)
rez_ega <- make_ega(data6f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data6f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
rez_cfa6  <- make_cfa(data6f)

@@

```{r data6f_details}
#| warning: false
#| message: false

@@

rez_cfa6$test
```

@@

```{r data7a}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data7a_details}
#| warning: false
#| message: false

@@

```{r data7af}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data7af_details}
#| warning: false
#| message: false

@@

```{r data7b}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data7b_details}
#| warning: false
#| message: false

@@

```{r data7bf_details}
#| warning: false
#| message: false

@@

rez_cfa7b$test
```

@@

```{r data7c}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data7c_details}
#| warning: false
#| message: false

@@

```{r data7cf_details}
#| warning: false
#| message: false

@@

rez_cfa7c$test
```

@@

```{r data8a}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data8a_details}
#| message: false
#| warning: false

@@

```{r data8af_details}
#| warning: false
#| message: false

@@

rez_cfa8a$test
```
::::

@@

```{r data8b}
#| warning: false
#| message: false
#| fig-width: 12
#| fig-height: 20

@@

```{r data8b_details}
#| warning: false
#| message: false

@@

```{r data8bf_details}
#| warning: false
#| message: false
